The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba

### 2020-11-25 analysis/paper/paper.Rmd
testing travis2

gettingRF <- function(alignedFasta){
  if (class(alignedFasta)!= c("DNAStringSet")){
    stop("This function only takes files of class 'DNAStringSet'. Use package 'Biostrings' to read the input file")
  }
  if (any(letterFrequency(alignedFasta, "-", as.prob=TRUE))>0){
    stop("This function do not take gaps as values/strings. Go and replaced gaps with Ns (if the gaps are at the begining or end of the sequences) or choose a subset of sequences that do not contain gaps")
  }
  # predORF() do not read seqs with gaps   # predicts longest ORF for sense strand in each query sequence               
  orf1 <- predORF(alignedFasta[1:10], n=1, type="df", mode="orf", strand="sense")                                       
  longestSeq1 <- orf1$start[orf1$width == max(orf1$width)]
  codonPosition1 <- longestSeq1[1]/3
  codonConfirmation1 <- round(codonPosition1)
  length(alignedFasta)
  if (codonPosition1==codonConfirmation1){
   file.rename("/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_7-gaps.fasta", "/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")                     # 640 bp
  print("The Reading Frame of these seqs is +1, no further action is required, go to modelTesting")
    } else {
    if (codonPosition1!=codonConfirmation1){
      tempLength <- length(alignedFasta[[1]])
      #remove first nucleotide position
      newRF2 <- subseq(alignedFasta, start = 2, end = tempLength)      # 639 bp
      # getting new RF from the new alignment with -1 bp.
      orf2 <- predORF(newRF2[1:10], n=1, type="df", mode="orf", strand="sense") 
      # checking size gain
      longestSeq2 <- orf2$start[orf2$width == max(orf2$width)]
      codonPosition2 <- (longestSeq2[1]+2)/3
      codonConfirmation2 <- round(codonPosition2)
      if (codonPosition2==codonConfirmation2){
        writeXStringSet(newRF2, file="/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")
      print("The Reading Frame of these seqs was +2, new fasta file created, go to modelTesting")
      } else {
      if (codonPosition2!=codonConfirmation2){
        #remove first nucleotide position
        tempLength <- length(alignedFasta[[1]])
        newRF3 <- subseq(alignedFasta, start = 3, end = tempLength)
        writeXStringSet(newRF3, file="/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")    # 638 bp
      print("The Reading Frame of these seqs was +3, new fasta file created, go to modelTesting")
     }
   }  
  }
 }
}

gettingRF(alignedFasta)

@@

gettingBestModel <- function(fastaRF){
  if (class(fastaRF)!= c("DNAbin")){
    stop("This function only takes files of class 'DNAbin'. Use package 'ape' to read the input file")
  }
  formatPhyDat <- as.phyDat(fastaRF)                #getting the class used by modelTest: phyDat or pml
  modelChoice <- modelTest(formatPhyDat, tree = NULL, model = c("JC", "K80", "HKY", "TrN", "SYM", "GTR"), multicore = TRUE, mc.cores = 4)
  modelChoiceSorted <- modelChoice[order(modelChoice$AICc),]
  return(modelChoiceSorted)
}

bestModel <- gettingBestModel(fastaRF)                # getting the AICc for each competing model

>>>>

getRF <- function(alignedFasta){
  if (class(alignedFasta)!= c("DNAStringSet")){
    stop("This function only takes files of class 'DNAStringSet'. Use package 'Biostrings' to read the input file")
  }
  if (any(letterFrequency(alignedFasta, "-", as.prob=TRUE))>0){
    stop("This function do not take gaps as values/strings. Go and replaced gaps with Ns (if the gaps are at the begining or end of the sequences) or choose a subset of sequences that do not contain gaps")
  }
  # predORF() do not read seqs with gaps   # predicts longest ORF for sense strand in each query sequence               
  orf1 <- predORF(alignedFasta[1:10], n=1, type="df", mode="orf", strand="sense")                                       
  longestSeq1 <- orf1$start[orf1$width == max(orf1$width)]
  codonPosition1 <- longestSeq1[1]/3
  codonConfirmation1 <- round(codonPosition1)
  length(alignedFasta)
  if (codonPosition1==codonConfirmation1){
   file.rename("/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_7-gaps.fasta", "/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")                     # 640 bp
  print("The Reading Frame of these seqs is +1, no further action is required, go to modelTesting")
    } else {
    if (codonPosition1!=codonConfirmation1){
      tempLength <- length(alignedFasta[[1]])
      #remove first nucleotide position
      newRF2 <- subseq(alignedFasta, start = 2, end = tempLength)      # 639 bp
      # getting new RF from the new alignment with -1 bp.
      orf2 <- predORF(newRF2[1:10], n=1, type="df", mode="orf", strand="sense") 
      # checking size gain
      longestSeq2 <- orf2$start[orf2$width == max(orf2$width)]
      codonPosition2 <- (longestSeq2[1]+2)/3
      codonConfirmation2 <- round(codonPosition2)
      if (codonPosition2==codonConfirmation2){
        writeXStringSet(newRF2, file="/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")
      print("The Reading Frame of these seqs was +2, new fasta file created, go to modelTesting")
      } else {
      if (codonPosition2!=codonConfirmation2){
        #remove first nucleotide position
        tempLength <- length(alignedFasta[[1]])
        newRF3 <- subseq(alignedFasta, start = 3, end = tempLength)
        writeXStringSet(newRF3, file="/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_newRF.fasta")    # 638 bp
      print("The Reading Frame of these seqs was +3, new fasta file created, go to modelTesting")
     }
   }  
  }
 }
}

getRF(alignedFasta)

@@

getBestModel <- function(fastaRF){
  if (class(fastaRF)!= c("DNAbin")){
    stop("This function only takes files of class 'DNAbin'. Use package 'ape' to read the input file")
  }
  formatPhyDat <- as.phyDat(fastaRF)                #getting the class used by modelTest: phyDat or pml
  modelChoice <- modelTest(formatPhyDat, tree = NULL, model = c("JC", "K80", "HKY", "TrN", "SYM", "GTR"), multicore = TRUE, mc.cores = 4)
  modelChoiceSorted <- modelChoice[order(modelChoice$AICc),]
  return(modelChoiceSorted)
}

bestModel <- getBestModel(fastaRF)                # getting the AICc for each competing model
